\documentclass[a4paper,10pt]{article}
\usepackage{latexsym}
\usepackage{enumitem}
\usepackage[colorlinks=true,urlcolor=blue,linkcolor=black]{hyperref}
\usepackage[margin=0.75in]{geometry}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{ragged2e} % For justified text in itemize

% Section formatting
\usepackage{titlesec}
\titleformat{\section}{\Large\bfseries}{}{0pt}{}[\titlerule]
\titlespacing*{\section}{0pt}{10pt}{8pt}

% No indent
\setlength{\parindent}{0pt}

% List spacing
\setlist[itemize]{nosep, topsep=3pt, leftmargin=*}
\setlength{\parskip}{6pt}

\linespread{1.05}

\begin{document}

%----------------------------------------------------------------------------------------
% HEADER SECTION
%----------------------------------------------------------------------------------------
\begin{center}
    {\Huge \textbf{John Doe}} \\
    \vspace{6pt}
    \textbf{Software Engineer} \\
    \vspace{3pt}
    \href{mailto:john.doe@email.com}{\faEnvelope\, john.doe@email.com} •
    \href{tel:+15551234567}{\faPhone\, +1-555-123-4567} •
    \href{https://linkedin.com/in/johndoe-linkedin}{\faLinkedin\, LinkedIn Profile URL} •
    \href{https://github.com/johndoe-github}{\faGithub\, GitHub Profile URL}
\end{center}

%----------------------------------------------------------------------------------------
% PROFESSIONAL SUMMARY SECTION
%----------------------------------------------------------------------------------------
\section*{Professional Summary}
Highly motivated and results-driven Software Engineer with 5+ years of experience in developing scalable web applications. Proven ability to lead teams and deliver projects on time and within budget.  Passionate about innovation and continuous learning in the field of software development.

%----------------------------------------------------------------------------------------
% CORE ACHIEVEMENTS SECTION
%----------------------------------------------------------------------------------------
\section*{Core Achievements}
\begin{itemize}
    \item Led development of 3 major software projects from concept to deployment.
    \item Increased team efficiency by 20\% through implementation of Agile methodologies.
    \item Reduced system downtime by 15\% by optimizing server performance.
    \item Mentored junior developers, fostering team growth and skill development.
    \item Consistently received positive performance reviews for exceeding project expectations.
\end{itemize}

%----------------------------------------------------------------------------------------
% PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------\section*{Professional Experience}

\textbf{Acme Corporation, Tech Company} \hfill City, State \\
\emph{Senior Software Engineer} \hfill June 2020 -- Present
\begin{itemize}
    \item Led a team of 5 engineers in the development of a new cloud-based platform.
    \item Implemented key features resulting in a 30\% increase in user engagement.
    \item Optimized database queries, improving application performance by 25\%.
    \item Collaborated with cross-functional teams to define product requirements and timelines.
    \item Provided technical guidance and mentorship to junior team members.
\end{itemize}

\textbf{Beta Solutions Inc.} \hfill Another City, State \\
\emph{Software Engineer} \hfill January 2018 -- May 2020
\begin{itemize}
    \item Developed and maintained RESTful APIs for web and mobile applications.
    \item Contributed to the design and implementation of a new microservices architecture.
    \item Wrote unit and integration tests to ensure code quality and reliability.
    \item Participated in code reviews and provided constructive feedback to team members.
    \item Troubleshooted and resolved production issues, minimizing system downtime.
\end{itemize}

%----------------------------------------------------------------------------------------
% TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------
\section*{Technical Skills}
\begin{itemize}
    \item \textbf{Programming Languages:} Python, Java, JavaScript, C++
    \item \textbf{Web Technologies:} HTML, CSS, React, Node.js, REST APIs
    \item \textbf{Databases:} SQL, MySQL, PostgreSQL, MongoDB
    \item \textbf{Cloud Platforms:} AWS, Google Cloud Platform, Azure
    \item \textbf{Tools \& Technologies:} Git, Docker, Kubernetes, Agile/Scrum, JIRA, Confluence
\end{itemize}

%----------------------------------------------------------------------------------------
% EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section*{Education}

\textbf{University of Example, State University} \hfill City, State \\
\textbf{Master of Science in Computer Science} \hfill May 2020
\begin{itemize}
    \item GPA: 3.8/4.0
    \item Relevant Coursework: Data Structures and Algorithms, Cloud Computing, Software Engineering, Database Systems    \item Thesis: "Scalable Algorithms for Real-Time Data Processing"
\end{itemize}

\textbf{State College} \hfill Another City, State \\
\textbf{Bachelor of Science in Software Engineering} \hfill May 2018

%----------------------------------------------------------------------------------------
% OPEN SOURCE PROJECTS SECTION
%----------------------------------------------------------------------------------------
\section*{Open Source Projects}
\begin{itemize}
    \item \href{https://example-portfolio.com}{Personal Portfolio Website}: Developed using React and Node.js, showcasing personal projects and skills.
    \item \href{https://github.com/johndoe-github}{GitHub Contributions}: Active contributor to open-source projects related to web development and data science.
    \item \href{https://github.com/project-repo}{Project "Data Analyzer"}: Python-based tool for analyzing large datasets, available on GitHub.
\end{itemize}

%----------------------------------------------------------------------------------------
% AWARDS & RECOGNITION SECTION
%----------------------------------------------------------------------------------------
\section*{Awards \& Recognition}
\begin{itemize}
    \item Dean's List, University of Example - Fall 2019, Spring 2020
    \item "Best Project" Award for Senior Design Project - May 2018
    \item Scholarship Recipient, [Scholarship Name] - 2016-2020
\end{itemize}

\vspace{5pt}
\small{Last Updated: February 13, 2025} % Update this date

\end{document}
